### 2011-04-05 docs/enthalpy/enthalpy.tex
Finished section of derviation energy equation .

We could then write,
\begin{eqnarray*}
\nabla \cdot \ubold &=& \frac{1}{\rho p_\rho} \left(
- \frac{D p}{D t} + \frac{p_T}{\rho c_p}
  \left( (1 - \rho h_p) \frac{D p}{D t} - \rho \sum_k \xi_k \omegadot_k + \rho \Hnuc \right)
+ \sum_k p_{X_k} \omegadot_k \right)  \\
                 &=& \frac{1}{\rho p_\rho}
  \left( \frac{p_T}{\rho c_p}(1  - \rho h_p) - 1 \right) \frac{D p}{D t}
 + \frac{1}{\rho p_\rho} \left(
  \frac{p_T}{\rho c_p} (\rho \Hnuc - \rho \sum_k \xi_k   \omegadot_k)
                               + \sum_k p_{X_k} \omegadot_k \right) \enskip .
\end{eqnarray*}
When we derived this expression we explicitly retained the dependence of $h$ on $p$,
as shown by the presence of the $h_p$ term.

Then, replacing $p$ by $p_0(r)$, $Dp/Dt$ becomes $\ubold \cdot
\nabla p_0$, and the divergence constraint can be written
\begin{equation}
\nabla \cdot \ubold + \alpha \ubold \cdot \nabla p_0 =
\frac{1}{\rho p_\rho} \left(
   \frac{p_T}{\rho c_p} \left(
  - \sum_k\rho  \xi_k \omegadot_k + \rho \Hnuc \right)
 + \sum_k p_{X_k} \omegadot_k \right)  \equiv \tilde{S} \enskip \label{eq:full_divu_constraint} ,
\end{equation}
where we define
\begin{equation}
\alpha(\rho,T) \equiv - \left( \frac{(1 - \rho h_p )p_T - \rho c_p}{\rho^2
  c_p p_\rho} \right) \enskip . \label{eq:alphadef}
\end{equation}

@@

Now writing $e = e(p,T,X_k)$ and expanding $De/Dt$ and using the energy evolution equation:
\begin{equation}
\rho \frac{D e}{Dt}  = \rho \left( e_p \frac{D p}{Dt} + c_v \frac{D T}{Dt} + \sum_k e_{X_k} \frac{D X_k}{Dt} \right)
                     = -p \nabla \cdot \Ub + \rho \Hnuc
\end{equation}
we can express $DT/Dt$ in terms of 
\begin{eqnarray*}
\frac{DT}{Dt} &=& \frac{1}{\rho c_v} \left(
                  -p \nabla \cdot \Ub + \rho \Hnuc
                 - \rho e_p \frac{D p}{Dt}
                 - \rho \sum_k e_{X_k} \omegadot_k   \right)
\end{eqnarray*}
where $c_v = \left.\partial e/\partial T\right|_{p,X_k}$ is the
specific heat at constant volume,
and $e_p = \left.\partial e/\partial p\right|_{T,X_k}.$
Then
\begin{equation}
-\rho \nabla \cdot \Ub = 
    \frac{1}{p_\rho} \left( \frac{D p}{Dt} 
    - \frac{p_T}{\rho c_v} \left(
                 -p \nabla \cdot \Ub + \rho \Hnuc
                 - \rho e_p \frac{D p}{Dt}
                 - \rho \sum_k e_{X_k} \omegadot_k   \right)
    - \sum_k p_{X_k} {\omegadot}_k \right) \enskip ,
\end{equation}
which leads to 
\begin{equation}
\left(-\rho -  \frac{p p_T}{\rho c_v p_\rho} \right) \nabla \cdot \Ub = 
    \frac{1}{p_\rho} \left( (1 + \frac{e_p p_T}{c_v}) \frac{D p}{Dt} 
                           - \frac{p_T}{\rho c_v} \left(
                                        \rho \Hnuc
                                        - \rho \sum_k e_{X_k} \omegadot_k   \right)
    - \sum_k p_{X_k} {\omegadot}_k \right) \enskip ,
\end{equation}

@@

If we set $\omegadot_k = \Hnuc = 0$ for simplicity, then the constraint as derived using $h$ can be written 
\begin{equation}
\nabla \cdot \ubold
- \left( \frac{(1 - \rho h_p )p_T - \rho c_p}{\rho^2
  c_p p_\rho} \right) \frac{D p_0}{D t} = 0
\end{equation}
and the constraint derived using $e$ can be written
\begin{equation}
\left(\rho p_\rho + \frac{p p_T}{\rho c_v} \right) \nabla \cdot \Ub +
      (1 + \frac{e_p p_T}{c_v}) \frac{D p}{Dt} = 0 \enskip .
\end{equation}

>>>>

We could then write,
\begin{eqnarray*}
\nabla \cdot \Ub &=& \frac{1}{\rho p_\rho} \left(
- \frac{D p}{D t} + \frac{p_T}{\rho c_p}
  \left( (1 - \rho h_p) \frac{D p}{D t} - \rho \sum_k \xi_k \omegadot_k + \rho \Hnuc \right)
+ \sum_k p_{X_k} \omegadot_k \right)  \\
                 &=& \frac{1}{\rho p_\rho}
  \left( \frac{p_T}{\rho c_p}(1  - \rho h_p) - 1 \right) \frac{D p}{D t}
 + \frac{1}{\rho p_\rho} \left(
  \frac{p_T}{\rho c_p} (\rho \Hnuc - \rho \sum_k \xi_k   \omegadot_k)
                               + \sum_k p_{X_k} \omegadot_k \right) \enskip .
\end{eqnarray*}
When we derived this expression we explicitly retained the dependence of $h$ on $p$,
as shown by the presence of the $h_p$ term.

Then, replacing $p$ by $p_0(r)$, $Dp/Dt$ becomes $\Ub \cdot
\nabla p_0$, and the divergence constraint can be written
\begin{equation}
\nabla \cdot \Ub + \alpha \Ub \cdot \nabla p_0 =
\frac{1}{\rho p_\rho} \left(
   \frac{p_T}{\rho c_p} \left(
  - \sum_k\rho  \xi_k \omegadot_k + \rho \Hnuc \right)
 + \sum_k p_{X_k} \omegadot_k \right)  \equiv \tilde{S} \enskip \label{eq:full_divu_constraint} ,
\end{equation}
where we define
\begin{equation}
\alpha(\rho,T) \equiv - \left( \frac{(1 - \rho h_p )p_T - \rho c_p}{\rho^2
  c_p p_\rho} \right) \enskip . \label{eq:alphadef}
\end{equation}

@@

Now writing $e = e(p,T,X_k)$ and expanding $De/Dt$ and using the energy evolution equation:
\begin{equation}
\rho \frac{D e}{Dt}  = \rho \left( e_p \frac{D p}{Dt} + e_T \frac{D T}{Dt} + \sum_k e_{X_k} \frac{D X_k}{Dt} \right)
                     = -p \nabla \cdot \Ub + \rho \Hnuc
\end{equation}
we can express $DT/Dt$ in terms of 
\begin{eqnarray*}
\frac{DT}{Dt} &=& \frac{1}{\rho e_T} \left(
                  -p \nabla \cdot \Ub + \rho \Hnuc
                 - \rho e_p \frac{D p}{Dt}
                 - \rho \sum_k e_{X_k} \omegadot_k   \right)
\end{eqnarray*}
where $e_T = \left.\partial e/\partial T\right|_{p,X_k}$ is the
specific heat at constant volume,
and $e_p = \left.\partial e/\partial p\right|_{T,X_k}.$
Then
\begin{equation}
-\rho \nabla \cdot \Ub = 
    \frac{1}{p_\rho} \left( \frac{D p}{Dt} 
    - \frac{p_T}{\rho e_T} \left(
                 -p \nabla \cdot \Ub + \rho \Hnuc
                 - \rho e_p \frac{D p}{Dt}
                 - \rho \sum_k e_{X_k} \omegadot_k   \right)
    - \sum_k p_{X_k} {\omegadot}_k \right) \enskip ,
\end{equation}
which leads to 
\begin{equation}
\left(-\rho -  \frac{p p_T}{\rho e_T p_\rho} \right) \nabla \cdot \Ub = 
    \frac{1}{p_\rho} \left( (1 + \frac{e_p p_T}{e_T}) \frac{D p}{Dt} 
                           - \frac{p_T}{\rho e_T} \left(
                                        \rho \Hnuc
                                        - \rho \sum_k e_{X_k} \omegadot_k   \right)
    - \sum_k p_{X_k} {\omegadot}_k \right) \enskip ,
\end{equation}

@@

If we set $\omegadot_k = \Hnuc = 0$ for simplicity, then the constraint as derived using $h$ can be written 
\begin{equation}
\nabla \cdot \Ub
- \left( \frac{(1 - \rho h_p )p_T - \rho c_p}{\rho^2
  c_p p_\rho} \right) \frac{D p_0}{D t} = 0
\end{equation}
and the constraint derived using $e$ can be written
\begin{equation}
\nabla \cdot \Ub 
+ \left( \frac{\rho e_T + \rho e_p p_T}{\rho^2 e_T p_\rho + p p_T} \right) \frac{D p_0}{D t} = 0
\end{equation}
